---
title: "Source Code for Multiple Imputation Comparisons: Individual Reports, SGP Summaries"
author: "Allie Cooperman, Adam Van Iwaarden, and Damian Betebenner"
date: "June 16, 2021"
output: html_document
params: 
    printcode: TRUE
    evalcode: FALSE
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(cache   = FALSE, 
                      eval    = params$evalcode,
                      echo    = params$printcode, 
                      message = FALSE, 
                      warning = FALSE,
                      fig.align = "center") 
```

````md

---
title: 'Imputation Method Performance: Student Growth Percentiles'
author: "AUTHOR"
date:  "`r "\u0060r format(Sys.time(), '%B %d, %Y')\u0060"`"
output: 
  html_document:
    theme: sandstone
    toc: true
    toc_float: true
    toc_depth: 4
    highlight: tango
---

## Summary Tables

In the following summary tables, cases where the percent bias is less than 5% and the coverage rate is greater than 0.90 are bolded.

### Grade by Content Area

```{r}`r ''`
# Create factor variable based on quantiles of grade/content area size
Imputation_Summary_All_Methods_GC[, N_QUANT := cut(N, breaks = c(quantile(N, seq(0, 1, by = 0.25))),
                                                   labels = c("0-25%", "25-50%", "50-75%", "75-100%"),
                                                   include.lowest = T)]
Imputation_Summary_All_Methods_Global[, N_QUANT := cut(N, breaks = c(quantile(N, seq(0, 1, by = 0.25))),
                                                   labels = c("0-25%", "25-50%", "50-75%", "75-100%"),
                                                   include.lowest = T)]

# Summary table by grade, content area, and imputation method
Summary_GradeContent = Imputation_Summary_All_Methods_GC[,.("mean_pctbias" = mean(SGP_Pct_Bias, na.rm = T),
                                     "mean_ci" = mean(SGP_Coverage_Simp, na.rm = T),
                                     "mean_rawbias" = mean(SGP_Raw_Bias, na.rm = T)),
                                       keyby = .(CONTENT_AREA, GRADE, 
                                                 IMP_METHOD)][,-1]
boldrows = which(Summary_GradeContent$mean_pctbias < 5 & Summary_GradeContent$mean_ci > 0.9)
kable(Summary_GradeContent, format = "html", digits = 3, col.names = c("Grade", "Imputation Method", "Mean Percent Bias", "Mean CI Coverage Rate", "Mean Raw Bias"),
      caption = "Summary statistics by content area, grade, and imputation method") %>%
   kable_styling(bootstrap_options = "striped", full_width = F)  %>%
   row_spec(boldrows, bold = T, color = "red") %>%
   pack_rows("ELA", 1, 36) %>%
   pack_rows("Mathematics", 37, 72) %>%
   scroll_box(height = "500px")
```

### School Size

```{r}`r ''`
# Summary table by N quantile and imputation method
Summary_GCArea = Imputation_Summary_All_Methods_GC[,.("mean_pctbias" = mean(SGP_Pct_Bias, na.rm = T),
                                                  "mean_ci" = mean(SGP_Coverage_Simp, na.rm = T),
                                                  "mean_rawbias" = mean(SGP_Raw_Bias, na.rm = T)),
                                                   keyby = .(N_QUANT, IMP_METHOD)]
boldrows = which(Summary_GCArea$mean_pctbias < 5 & Summary_GCArea$mean_ci > 0.9)
kable(Summary_GCArea, format = "html", digits = 3, col.names = c("Grade/Content Area Size Quantile", "Imputation Method", 
                                                   "Mean Percent Bias", "Mean CI Coverage Rate", "Mean Raw Bias"),
        caption = "Summary statistics by grade/content area size quantile and imputation method") %>%
   kable_styling(bootstrap_options = "striped", full_width = F)  %>%
   row_spec(boldrows, bold = T, color = "red") %>%
   scroll_box(height = "500px")
```

```{r}`r ''`
# Summary table by N quantile and imputation method
Summary_SchoolSize = Imputation_Summary_All_Methods_Global[,.("mean_pctbias" = mean(SGP_Pct_Bias, na.rm = T),
                                                          "mean_ci" = mean(SGP_Coverage_Simp, na.rm = T),
                                                          "mean_rawbias" = mean(SGP_Raw_Bias, na.rm = T)),
                                                           keyby = .(N_QUANT, IMP_METHOD)] 
boldrows = which(Summary_SchoolSize$mean_pctbias < 5 & Summary_SchoolSize$mean_ci > 0.9)
kable(Summary_SchoolSize, format = "html", digits = 3, col.names = c("Aggregated School Size Quantile", "Imputation Method", 
                                                   "Mean Percent Bias", "Mean CI Coverage Rate", "Mean Raw Bias"),
        caption = "Summary statistics by grade/content area size quantile and imputation method") %>%
   kable_styling(bootstrap_options = "striped", full_width = F)  %>%
   row_spec(boldrows, bold = T, color = "red") %>%
   scroll_box(height = "500px")
```

## Raw Bias

```{r outwidth = "80%", fig.align = "center"}`r ''`
# Box plot of raw bias
ggplot(Imputation_Summary_All_Methods_GC, aes(x = IMP_METHOD, y = SGP_Raw_Bias)) +
  geom_boxplot() + coord_flip() +
  labs(x = "Imputation Method", y = "Raw Scale Score Bias (Imputed - Complete)") +
  ggtitle("Raw Scale Score Bias By Imputation Method") +
  theme(plot.title = element_text(hjust = 0.5)) + 
  ylim(c(-40, 40))
```

### Grade by Content Area

```{r out.width = "80%", fig.align = "center"}`r ''`
# Box plot of raw bias, faceting by grade
ggplot(Imputation_Summary_All_Methods_GC, aes(x = GRADE, y = SGP_Raw_Bias, fill = IMP_METHOD)) +
  geom_boxplot() + coord_flip() +
  labs(x = "Grade", y = "Raw Scale Score Bias (Imputed - Complete)") +
  ggtitle("Raw Scale Score Bias By Grade and Imputation Method") +
  guides(fill = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_fill_brewer(palette="Dark2") + 
  ylim(c(-40, 40))

# Box plot of raw bias, faceting by content area
ggplot(Imputation_Summary_All_Methods_GC, aes(x = CONTENT_AREA, y = SGP_Raw_Bias, fill = IMP_METHOD)) +
  geom_boxplot() + coord_flip() +
  labs(x = "Content Area", y = "Raw Scale Score Bias (Imputed - Complete)") +
  ggtitle("Raw Scale Score Bias By Content Area and Imputation Method") +
  guides(fill = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_fill_brewer(palette="Dark2") + 
  ylim(c(-40, 40))

# Box plot of raw bias, faceting by grade and content area
ggplot(Imputation_Summary_All_Methods_GC, aes(x = CONTENT_AREA, y = SGP_Raw_Bias, fill = IMP_METHOD)) +
  geom_boxplot() + coord_flip() +
  labs(x = "Content Area", y = "Raw Scale Score Bias (Imputed - Complete)") +
  ggtitle("Raw Scale Score Bias By Grade, Content Area, and Imputation Method") +
  facet_wrap(~GRADE) +
  guides(fill = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_fill_brewer(palette="Dark2") + 
  ylim(c(-40, 40))
```

### School Size

We next examine raw bias as a function of the school size. School size is either partitioned by grade/content area ($N_{GC}$) or aggregated at the full school level ($N_S$).

```{r outwidth = "80%"}`r ''`
# Scatterplot of raw bias as a function of N
# Using different colors for imputation method
Imputation_Summary_All_Methods_GC[order(N)] %>%
ggplot(aes(x = N, y = SGP_Raw_Bias, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Grade/Content Area Size", y = "Raw Scale Score Bias (Imputed - Complete)") +
  ggtitle("Raw Scale Score Bias \nAs a Function of Grade/Content Area School Size") +
  guides(color = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2") +
  geom_hline(aes(yintercept = 0), color = "#999999")

# Scatterplot of raw bias as a function of N
# Faceting by imputation method
Imputation_Summary_All_Methods_GC[order(N)] %>%
ggplot(aes(x = N, y = SGP_Raw_Bias, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Grade/Content Area Size", y = "Raw Scale Score Bias (Imputed - Complete)") +
  ggtitle("Raw Scale Score Bias \nAs a Function of Grade/Content Area School Size \nFaceting by Imputation Method") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2") +
  geom_hline(aes(yintercept = 0), color = "#999999")

# Scatterplot of conditional mean raw bias based on grade/content area size
Imputation_Summary_All_Methods_GC[, .("condmean" = mean(SGP_Raw_Bias)), keyby = .(N, IMP_METHOD)] %>%
  ggplot(aes(x = N, y = condmean, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Grade/Content Area Size", y = "Conditional Mean Raw Bias") +
  ggtitle("Mean Raw Scale Score Bias \nConditioning on Grade/Content Area Size") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")

# Scatterplot of average bias as a function of aggregated N
# Using different colors for imputation method
ggplot(Imputation_Summary_All_Methods_Global, aes(x = N, y = SGP_Raw_Bias, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Aggregated School Size (Summing across Grade and Content Area)", y = "Raw Scale Score Bias (Imputed - Complete)") +
  ggtitle("Mean Scale Score Bias \nAs a Function of Aggregated School Size") +
  guides(color = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2") +
  geom_hline(aes(yintercept = 0), color = "#999999")

# Scatterplot of average bias as a function of aggregated N
# Faceting by imputation method
ggplot(Imputation_Summary_All_Methods_Global, aes(x = N, y = SGP_Raw_Bias, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Aggregated School Size (Summing across Grade and Content Area)", y = "Raw Scale Score Bias (Imputed - Complete)") +
  ggtitle("Mean Scale Score Bias \nAs a Function of Aggregated School Size \nFaceting by Imputation Method") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2") +
  geom_hline(aes(yintercept = 0), color = "#999999")

# Scatterplot of conditional mean raw bias based on grade/content area size
Imputation_Summary_All_Methods_Global[, .("condmean" = mean(SGP_Raw_Bias)), keyby = .(N, IMP_METHOD)] %>%
  ggplot(aes(x = N, y = condmean, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Aggregated School Size (Summing across Grade and Content Area)", y = "Conditional Mean Raw Bias") +
  ggtitle("Mean Raw Scale Score Bias \nConditioning on Aggregated School Size") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")

# Scatterplot of absolute bias as a function of N
# Using different colors for imputation method
Imputation_Summary_All_Methods_GC[order(N)] %>%
ggplot(aes(x = N, y = abs(SGP_Raw_Bias), color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Grade/Content Area Size", y = "Absolute Scale Score Bias (|Imputed - Complete|)") +
  ggtitle("Absolute Scale Score Bias \nAs a Function of Grade/Content Area School Size") +
  guides(color = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")

# Scatterplot of absolute bias as a function of N
# Faceting by imputation method
Imputation_Summary_All_Methods_GC[order(N)] %>%
ggplot(aes(x = N, y = abs(SGP_Raw_Bias), color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Grade/Content Area Size", y = "Absolute Scale Score Bias (|Imputed - Complete|)") +
  ggtitle("Absolute Scale Score Bias \nAs a Function of Grade/Content Area School Size \nFaceting by Imputation Method") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")

# Scatterplot of conditional mean absolute bias based on grade/content area size
Imputation_Summary_All_Methods_GC[, .("condmean" = mean(abs(SGP_Raw_Bias))), keyby = .(N, IMP_METHOD)] %>%
  ggplot(aes(x = N, y = condmean, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Grade/Content Area Size", y = "Conditional Mean Absolute Bias") +
  ggtitle("Mean Absolute Scale Score Bias \nConditioning on Grade/Content Area Size") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")

# Scatterplot of average bias as a function of aggregated N
# Using different colors for imputation method
ggplot(Imputation_Summary_All_Methods_Global, aes(x = N, y = abs(SGP_Raw_Bias), color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Aggregated School Size (Summing across Grade and Content Area)", y = "Absolute Scale Score Bias (|Imputed - Complete|)") +
  ggtitle("Mean Absolute Scale Score Bias \nAs a Function of Aggregated School Size") +
  guides(color = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")

# Scatterplot of average absolute bias as a function of aggregated N
# Faceting by imputation method
ggplot(Imputation_Summary_All_Methods_Global, aes(x = N, y = abs(SGP_Raw_Bias), color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Aggregated School Size (Summing across Grade and Content Area)", y = "Absolute Scale Score Bias (|Imputed - Complete|)") +
  ggtitle("Mean Absolute Scale Score Bias \nAs a Function of Aggregated School Size \nFaceting by Imputation Method") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")

# Scatterplot of conditional mean absolute bias based on school size
Imputation_Summary_All_Methods_Global[, .("condmean" = mean(abs(SGP_Raw_Bias))), keyby = .(N, IMP_METHOD)] %>%
  ggplot(aes(x = N, y = condmean, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Aggregated School Size (Summing across Grade and Content Area)", y = "Conditional Mean Absolute Bias") +
  ggtitle("Mean Absolute Scale Score Bias \nConditioning on Aggregated School Size") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")
```

Next, we can further facet by grade.

```{r outwidth = "80%"}`r ''`
# Scatterplot of raw bias by N
# Facet by grade
Imputation_Summary_All_Methods_GC[order(N)] %>%
ggplot(aes(x = N, y = SGP_Raw_Bias, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Grade/Content Area Size", y = "Raw Scale Score Bias (Imputed - Complete)") +
  ggtitle("Raw Scale Score Bias \nAs a Function of Grade/Content Area School Size \nFaceting by Grade") +
  guides(color = guide_legend(title = "Imputation \nMethod")) +
  facet_wrap(~GRADE) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2") +
  geom_hline(aes(yintercept = 0), color = "#999999")

# Scatterplot of absolute bias by N
# Facet by grade
Imputation_Summary_All_Methods_GC[order(N)] %>%
ggplot(aes(x = N, y = abs(SGP_Raw_Bias), color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Grade/Content Area Size", y = "Absolute Scale Score Bias (|Imputed - Complete|)") +
  ggtitle("Absolute Scale Score Bias \nAs a Function of Grade/Content Area School Size \nFaceting by Grade") +
  guides(color = guide_legend(title = "Imputation \nMethod")) +
  facet_wrap(~GRADE) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")
```

### Percent Missing

```{r outwidth = "80%"}`r ''`
# Scatterplot of raw bias as a function of percent missing
# Using different colors for imputation method
Imputation_Summary_All_Methods_GC[order(Percent_Missing)] %>%
ggplot(aes(x = Percent_Missing, y = SGP_Raw_Bias, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Percentage Missing", y = "Raw Scale Score Bias (Imputed - Complete)") +
  ggtitle("Raw Scale Score Bias \nAs a Function of Percentage Missing") +
  guides(color = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2") +
  geom_hline(aes(yintercept = 0), color = "#999999")

# Scatterplot of raw bias as a function of percent missing
# Faceting by imputation method
Imputation_Summary_All_Methods_GC[order(Percent_Missing)] %>%
ggplot(aes(x = Percent_Missing, y = SGP_Raw_Bias, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Percentage Missing", y = "Raw Scale Score Bias (Imputed - Complete)") +
  ggtitle("Raw Scale Score Bias \nAs a Function of Percentage Missing \nFaceting by Imputation Method") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2") +
  geom_hline(aes(yintercept = 0), color = "#999999")

# Scatterplot of absolute bias as a function of percent missing
# Using different colors for imputation method
Imputation_Summary_All_Methods_GC[order(Percent_Missing)] %>%
ggplot(aes(x = Percent_Missing, y = abs(SGP_Raw_Bias), color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Percentage Missing", y = "Absolute Scale Score Bias (|Imputed - Complete|)") +
  ggtitle("Absolute Scale Score Bias \nAs a Function of Percentage Missing") +
  guides(color = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")

# Scatterplot of absolute bias as a function of N
# Faceting by imputation method
Imputation_Summary_All_Methods_GC[order(Percent_Missing)] %>%
ggplot(aes(x = Percent_Missing, y = abs(SGP_Raw_Bias), color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Percentage Missing", y = "Absolute Scale Score Bias (|Imputed - Complete|)") +
  ggtitle("Absolute Scale Score Bias \nAs a Function of Percentage Missing \nFaceting by Imputation Method") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")

# Scatterplot of raw bias by percent missing
# Facet by grade
Imputation_Summary_All_Methods_GC[order(Percent_Missing)] %>%
ggplot(aes(x = Percent_Missing, y = SGP_Raw_Bias, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Grade/Content Area Size", y = "Raw Scale Score Bias (Imputed - Complete)") +
  ggtitle("Raw Scale Score Bias \nAs a Function of Percentage Missing \nFaceting by Grade") +
  guides(color = guide_legend(title = "Imputation \nMethod")) +
  facet_wrap(~GRADE) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2") +
  geom_hline(aes(yintercept = 0), color = "#999999")

# Scatterplot of absolute bias by percent missing
# Facet by grade
Imputation_Summary_All_Methods_GC[order(Percent_Missing)] %>%
ggplot(aes(x = Percent_Missing, y = abs(SGP_Raw_Bias), color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Grade/Content Area Size", y = "Absolute Scale Score Bias (|Imputed - Complete|)") +
  ggtitle("Absolute Scale Score Bias \nAs a Function of Percentage Missing \nFaceting by Grade") +
  guides(color = guide_legend(title = "Imputation \nMethod")) +
  facet_wrap(~GRADE) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")

# Bubble chart with N and percent missing
# Faceting by imputation method
Imputation_Summary_All_Methods_GC[order(N)] %>%
ggplot(aes(x = N, y = SGP_Raw_Bias, color = IMP_METHOD)) +
  geom_point(aes(color = IMP_METHOD, size = Percent_Missing, alpha = 0.6)) +
  labs(x = "School Size (By Grade and Content Area)", y = "Raw Scale Score Bias (Imputed - Complete)") +
  ggtitle("Raw Scale Score Bias \nAs a Function of Grade/Content Area School Size and Percent Missing") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2") +
  geom_hline(aes(yintercept = 0), color = "#999999")

# Bubble chart with aggregated N and percent missing
# Faceting by imputation method
ggplot(Imputation_Summary_All_Methods_Global, aes(x = N, y = SGP_Raw_Bias, color = IMP_METHOD)) +
  geom_point(aes(color = IMP_METHOD, size = Percent_Missing, alpha = 0.6)) +
  labs(x = "Aggregated School Size (Summing across Grade and Content Area)", y = "Raw Scale Score Bias (Imputed - Complete)") +
  ggtitle("Raw Scale Score Bias \nAs a Function of Aggregated School Size and Average Percent Missing") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2") +
  geom_hline(aes(yintercept = 0), color = "#999999")
```

## Simplified CI Coverage Rates

```{r outwidth = "80%", fig.align = "center"}`r ''`
# Box plot of simplified CI coverage
ggplot(Imputation_Summary_All_Methods_GC, aes(x = IMP_METHOD, y = SGP_Coverage_Simp)) +
  geom_boxplot() + coord_flip() +
  labs(x = "Imputation Method", y = "Simplified CI Coverage") +
  ggtitle("Simplified CI Coverage By Imputation Method") +
  theme(plot.title = element_text(hjust = 0.5)) 
```

### Grade by Content Area

```{r out.width = "80%", fig.align = "center"}`r ''`
# Box plot of simplified CI coverage, faceting by grade
ggplot(Imputation_Summary_All_Methods_GC, aes(x = GRADE, y = SGP_Coverage_Simp, fill = IMP_METHOD)) +
  geom_boxplot() + coord_flip() +
  labs(x = "Grade", y = "Simplified CI Coverage Rate") +
  ggtitle("Simplified CI Coverage Rate By Grade and Imputation Method") +
  guides(fill = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_fill_brewer(palette="Dark2") 

# Box plot of simplified CI coverage, faceting by content area
ggplot(Imputation_Summary_All_Methods_GC, aes(x = CONTENT_AREA, y = SGP_Coverage_Simp, fill = IMP_METHOD)) +
  geom_boxplot() + coord_flip() +
  labs(x = "Content Area", y = "Simplified CI Coverage Rate") +
  ggtitle("Simplified CI Coverage Rate By Content Area and Imputation Method") +
  guides(fill = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_fill_brewer(palette="Dark2") 

# Box plot of simplified CI coverage, faceting by grade and content area
ggplot(Imputation_Summary_All_Methods_GC, aes(x = CONTENT_AREA, y = SGP_Coverage_Simp, fill = IMP_METHOD)) +
  geom_boxplot() + coord_flip() +
  labs(x = "Content Area", y = "Simplified CI Coverage Rate") +
  ggtitle("Simplified CI Coverage Rate By \nGrade, Content Area, and Imputation Method") +
  facet_wrap(~GRADE) +
  guides(fill = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_fill_brewer(palette="Dark2") 
```

### School Size

```{r outwidth = "80%"}`r ''`
# Scatterplot of average coverage rate as a function of aggregated N
# Using different colors for imputation method
ggplot(Imputation_Summary_All_Methods_Global, aes(x = N, y = SGP_Coverage_Simp, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Aggregated School Size (Summing across Grade and Content Area)", y = "Simplified CI Coverage Rate") +
  ggtitle("Simplified CI Coverage Rate \nAs a Function of Aggregated School Size") +
  guides(color = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")

# Scatterplot of average coverage rate as a function of aggregated N
# Faceting by imputation method
ggplot(Imputation_Summary_All_Methods_Global, aes(x = N, y = SGP_Coverage_Simp, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Aggregated School Size (Summing across Grade and Content Area)", y = "Simplified CI Coverage Rate") +
  ggtitle("Simplified CI Coverage Rate \nAs a Function of Aggregated School Size \nFaceting by Imputation Method") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")

# Scatterplot of conditional mean coverage rate based on school size
Imputation_Summary_All_Methods_Global[, .("condmean" = mean(SGP_Coverage_Simp)), keyby = .(N, IMP_METHOD)] %>%
  ggplot(aes(x = N, y = condmean, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Aggregated School Size (Summing across Grade and Content Area)", y = "Conditional Mean Raw Bias") +
  ggtitle("Mean Simplified CI Coverage Rate \nConditioning on Aggregated School Size") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")
```

### Percent Missing

Next, we look at simplified CI coverage rate as a function of the percent missing. 

```{r outwidth = "80%"}`r ''`
# Scatterplot of simplified CI coverage rate as a function of percent missing
# Using different colors for imputation method
Imputation_Summary_All_Methods_GC[order(Percent_Missing)] %>%
ggplot(aes(x = Percent_Missing, y = SGP_Coverage_Simp, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Percentage Missing", y = "Simplified CI Coverage Rate") +
  ggtitle("Simplified CI Coverage Rate \nAs a Function of Percentage Missing") +
  guides(color = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")

# Scatterplot of simplified CI coverage rate as a function of percent missing
# Faceting by imputation method
Imputation_Summary_All_Methods_GC[order(Percent_Missing)] %>%
ggplot(aes(x = Percent_Missing, y = SGP_Coverage_Simp, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Percentage Missing", y = "Simplified CI Coverage Rate") +
  ggtitle("Simplified CI Coverage Rate \nAs a Function of Percentage Missing \nFaceting by Imputation Method") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")

# Bubble chart with aggregated N and percent missing
# Faceting by imputation method
ggplot(Imputation_Summary_All_Methods_Global, aes(x = N, y = SGP_Coverage_Simp, color = IMP_METHOD)) +
  geom_point(aes(color = IMP_METHOD, size = Percent_Missing, alpha = 0.6)) +
  labs(x = "Aggregated School Size (Summing across Grade and Content Area)", y = "Simplified CI Coverage Rate") +
  ggtitle("Simplified CI Coverage Rate \nAs a Function of Aggregated School Size and Average Percent Missing") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")
```

## Percent Bias

```{r outwidth = "80%", fig.align = "center"}`r ''`
# Box plot of percent bias
ggplot(Imputation_Summary_All_Methods_GC, aes(x = IMP_METHOD, y = SGP_Pct_Bias)) +
  geom_boxplot() + coord_flip() +
  labs(x = "Imputation Method", y = "Percent Bias (%)") +
  ggtitle("Percent Bias By Imputation Method") +
  theme(plot.title = element_text(hjust = 0.5)) 
```

### Grade by Content Area

```{r out.width = "80%", fig.align = "center"}`r ''`
# Box plot of percent bias, faceting by grade
ggplot(Imputation_Summary_All_Methods_GC, aes(x = GRADE, y = SGP_Pct_Bias, fill = IMP_METHOD)) +
  geom_boxplot() + coord_flip() +
  labs(x = "Grade", y = "Percent Bias (%)") +
  ggtitle("Percent Bias By Grade and Imputation Method") +
  guides(fill = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_fill_brewer(palette="Dark2") 

# Box plot of percent bias, faceting by content area
ggplot(Imputation_Summary_All_Methods_GC, aes(x = CONTENT_AREA, y = SGP_Pct_Bias, fill = IMP_METHOD)) +
  geom_boxplot() + coord_flip() +
  labs(x = "Content Area", y = "Percent Bias (%)") +
  ggtitle("Percent Bias By Content Area and Imputation Method") +
  guides(fill = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_fill_brewer(palette="Dark2") 

# Box plot of percent bias, faceting by grade and content area
ggplot(Imputation_Summary_All_Methods_GC, aes(x = CONTENT_AREA, y = SGP_Pct_Bias, fill = IMP_METHOD)) +
  geom_boxplot() + coord_flip() +
  labs(x = "Content Area", y = "Percent Bias (%)") +
  ggtitle("Percent Bias By \nGrade, Content Area, and Imputation Method") +
  facet_wrap(~GRADE) +
  guides(fill = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_fill_brewer(palette="Dark2") 
```

### School Size

We next examine percent bias as a function of the school size. Here, school size is again only aggregated at the full school level ($N_S$). 

```{r outwidth = "80%"}`r ''`
# Scatterplot of average SS percent bias as a function of aggregated N
# Using different colors for imputation method
ggplot(Imputation_Summary_All_Methods_Global, aes(x = N, y = SGP_Pct_Bias, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Aggregated School Size (Summing across Grade and Content Area)", y = "Percent Bias (%)") +
  ggtitle("Percent Bias \nAs a Function of Aggregated School Size") +
  guides(color = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")

# Scatterplot of average SS percent bias as a function of aggregated N
# Faceting by imputation method
ggplot(Imputation_Summary_All_Methods_Global, aes(x = N, y = SGP_Pct_Bias, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Aggregated School Size (Summing across Grade and Content Area)", y = "Percent Bias (%)") +
  ggtitle("Percent Bias \nAs a Function of Aggregated School Size \nFaceting by Imputation Method") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")

# Scatterplot of conditional mean percent bias based on school size
Imputation_Summary_All_Methods_Global[, .("condmean" = mean(SGP_Pct_Bias)), keyby = .(N, IMP_METHOD)] %>%
  ggplot(aes(x = N, y = condmean, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Aggregated School Size (Summing across Grade and Content Area)", y = "Conditional Mean Raw Bias") +
  ggtitle("Mean Percent Bias \nConditioning on Aggregated School Size") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")
```

### Percent Missing

We now look at percent bias as a function of the percent missing. 

```{r outwidth = "80%"}`r ''`
# Scatterplot of percent bias as a function of percent missing
# Using different colors for imputation method
Imputation_Summary_All_Methods_GC[order(Percent_Missing)] %>%
ggplot(aes(x = Percent_Missing, y = SGP_Pct_Bias, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Percentage Missing", y = "Percent Bias (%)") +
  ggtitle("Percent Bias \nAs a Function of Percentage Missing") +
  guides(color = guide_legend(title = "Imputation \nMethod")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")

# Scatterplot of percent bias as a function of percent missing
# Faceting by imputation method
Imputation_Summary_All_Methods_GC[order(Percent_Missing)] %>%
ggplot(aes(x = Percent_Missing, y = SGP_Pct_Bias, color = IMP_METHOD)) +
  geom_point() +
  labs(x = "Percentage Missing", y = "Percent Bias (%)") +
  ggtitle("Percent Bias \nAs a Function of Percentage Missing \nFaceting by Imputation Method") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")

# Bubble chart with aggregated N and percent missing
# Faceting by imputation method
ggplot(Imputation_Summary_All_Methods_Global, aes(x = N, y = SGP_Pct_Bias, color = IMP_METHOD)) +
  geom_point(aes(color = IMP_METHOD, size = Percent_Missing, alpha = 0.6)) +
  labs(x = "Aggregated School Size (Summing across Grade and Content Area)", y = "Percent Bias (%)") +
  ggtitle("Percent Bias \nAs a Function of Aggregated School Size and Average Percent Missing") +
  theme(legend.position = "none") +
  facet_wrap(~IMP_METHOD) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_color_brewer(palette="Dark2")
```

## Explanatory Analyses

### Raw Bias

Here, we fit a series of linear fixed-effects regression models using the `fixest` package (Berge, 2018). The outcome of interest is raw bias, and three sets of predictors are examined: (a) imputation method only, (b) an additive model with imputation method, grade/content area or school size, and percentage missing, and (c) two-way interactions among the predictors in model B. The first set of models analyzes data at the grade/content area level. 

```{r echo = T}`r ''`
# Fit models
gc.raw.imp = feols(SGP_Raw_Bias ~ i(IMP_METHOD, ref = "Observed") | 
                   CONTENT_AREA^GRADE, Imputation_Summary_All_Methods_GC)
gc.raw.add = feols(SGP_Raw_Bias ~ N + Percent_Missing + i(IMP_METHOD, ref = "Observed") | 
                   CONTENT_AREA^GRADE, 
                   Imputation_Summary_All_Methods_GC)
gc.raw.int = feols(SGP_Raw_Bias ~ (N + Percent_Missing + i(IMP_METHOD, ref = "Observed"))^2 | 
                   CONTENT_AREA^GRADE, 
                   Imputation_Summary_All_Methods_GC)
```

```{r}`r ''`
# Create table of results
etable(gc.raw.imp, gc.raw.add, gc.raw.int, subtitles = c("A", "B", "C"),
       fitstat = c('r2', 'ar2', 'war2', 'aic', 'bic'))[-c(1,2),] %>%
  kable(format = "html", booktabs = T, row.names = T,
        col.names = c("Imputation Method Only", "Additive Model", "Interaction Model"),
        caption = "Linear fixed-effect regression models for raw bias at the grade/content area level") %>%
  kable_classic_2("hover", full_width = F) %>%
  scroll_box(height = "700px")
```

$~$

The next set of models analyzes data at the school level.

```{r echo = T}`r ''`
# Fit models
sc.raw.imp = feols(SGP_Raw_Bias ~ i(IMP_METHOD, ref = "Observed"), 
                   Imputation_Summary_All_Methods_Global)
sc.raw.add = feols(SGP_Raw_Bias ~ N + Percent_Missing + i(IMP_METHOD, ref = "Observed"), 
                   Imputation_Summary_All_Methods_Global)
sc.raw.int = feols(SGP_Raw_Bias ~ (N + Percent_Missing + i(IMP_METHOD, ref = "Observed"))^2, 
                   Imputation_Summary_All_Methods_Global)
```

```{r}`r ''`
# Create table of results
etable(sc.raw.imp, sc.raw.add, sc.raw.int, subtitles = c("A", "B", "C"),
       fitstat = c('r2', 'ar2', 'war2', 'aic', 'bic'))[-c(1,2),] %>%
  kable(format = "html", booktabs = T, row.names = T,
        col.names = c("Imputation Method Only", "Additive Model", "Interaction Model"),
        caption = "Linear fixed-effect regression models for raw bias at the school level") %>%
  kable_classic_2("hover", full_width = F) %>%
  scroll_box(height = "700px")
```

### Absolute Bias

Now, absolute rather than raw bias is used to better understand the relationships among the aforementioned factors on the magnitude of differences between the true and imputed mean values. 

```{r echo = T}`r ''`
# Fit models
gc.abs.imp = feols(abs(SGP_Raw_Bias) ~ i(IMP_METHOD, ref = "Observed") | 
                   CONTENT_AREA^GRADE, Imputation_Summary_All_Methods_GC)
gc.abs.add = feols(abs(SGP_Raw_Bias) ~ N + Percent_Missing + i(IMP_METHOD, ref = "Observed") | 
                   CONTENT_AREA^GRADE, 
                   Imputation_Summary_All_Methods_GC)
gc.abs.int = feols(abs(SGP_Raw_Bias) ~ (N + Percent_Missing + i(IMP_METHOD, ref = "Observed"))^2 | 
                   CONTENT_AREA^GRADE, 
                   Imputation_Summary_All_Methods_GC)
```

```{r}`r ''`
# Create table of results
etable(gc.abs.imp, gc.abs.add, gc.abs.int, subtitles = c("A", "B", "C"),
       fitstat = c('r2', 'ar2', 'war2', 'aic', 'bic'))[-c(1,2),] %>%
  kable(format = "html", booktabs = T, row.names = T,
        col.names = c("Imputation Method Only", "Additive Model", "Interaction Model"),
        caption = "Linear fixed-effect regression models for absolute bias at the grade/content area level") %>%
  kable_classic_2("hover", full_width = F) %>%
  scroll_box(height = "700px")
```

```{r echo = T}`r ''`
# Fit models
sc.abs.imp = feols(abs(SGP_Raw_Bias) ~ i(IMP_METHOD, ref = "Observed"), 
                   Imputation_Summary_All_Methods_Global)
sc.abs.add = feols(abs(SGP_Raw_Bias) ~ N + Percent_Missing + i(IMP_METHOD, ref = "Observed"), 
                   Imputation_Summary_All_Methods_Global)
sc.abs.int = feols(abs(SGP_Raw_Bias) ~ (N + Percent_Missing + i(IMP_METHOD, ref = "Observed"))^2, 
                   Imputation_Summary_All_Methods_Global)
```

```{r}`r ''`
# Create table of results
etable(sc.abs.imp, sc.abs.add, sc.abs.int, subtitles = c("A", "B", "C"),
       fitstat = c('r2', 'ar2', 'war2', 'aic', 'bic'))[-c(1,2),] %>%
  kable(format = "html", booktabs = T, row.names = T,
        col.names = c("Imputation Method Only", "Additive Model", "Interaction Model"),
        caption = "Linear fixed-effect regression models for absolute bias at the school level") %>%
  kable_classic_2("hover", full_width = F) %>%
  scroll_box(height = "700px")
```

### Coverage Rate 

In the final section, the outcome of interest is the simplified CI coverage rate. With this outcome variable, logistic rather than linear fixed effects models are fit to the data.

```{r echo = T}`r ''`
# Fit models
gc.cov.imp = feglm(SGP_Coverage_Simp ~ i(IMP_METHOD, ref = "Observed") | 
                   CONTENT_AREA^GRADE, 
                   Imputation_Summary_All_Methods_GC, family = "binomial")
gc.cov.add = feglm(SGP_Coverage_Simp ~ N + Percent_Missing + i(IMP_METHOD, ref = "Observed") | 
                   CONTENT_AREA^GRADE, 
                   Imputation_Summary_All_Methods_GC, family = "binomial")
gc.cov.int = feglm(SGP_Coverage_Simp ~ (N + Percent_Missing + i(IMP_METHOD, ref = "Observed"))^2 | 
                   CONTENT_AREA^GRADE, 
                   Imputation_Summary_All_Methods_GC, family = "binomial")
```

```{r}`r ''`
# Create table of results
etable(gc.cov.imp, gc.cov.add, gc.cov.int, subtitles = c("A", "B", "C"),
       fitstat = c('aic', 'bic'))[-c(1,2),] %>%
  kable(format = "html", booktabs = T, row.names = T,
        col.names = c("Imputation Method Only", "Additive Model", "Interaction Model"),
        caption = "Logistic fixed-effect regression models for CI coverage rate at the grade/content area level") %>%
  kable_classic_2("hover", full_width = F) %>%
  scroll_box(height = "700px")
```

```{r echo = T}`r ''`
# Fit models
sc.cov.imp = feglm(SGP_Coverage_Simp ~ i(IMP_METHOD, ref = "Observed"), 
                   Imputation_Summary_All_Methods_Global, family = "binomial")
sc.cov.add = feglm(SGP_Coverage_Simp ~ N + Percent_Missing + i(IMP_METHOD, ref = "Observed"), 
                   Imputation_Summary_All_Methods_Global, family = "binomial")
sc.cov.int = feglm(SGP_Coverage_Simp ~ (N + Percent_Missing + i(IMP_METHOD, ref = "Observed"))^2, 
                   Imputation_Summary_All_Methods_Global, family = "binomial")
```

```{r}`r ''`
# Create table of results
etable(sc.cov.imp, sc.cov.add, sc.cov.int, subtitles = c("A", "B", "C"),
       fitstat = c('aic', 'bic'))[-c(1,2),] %>%
  kable(format = "html", booktabs = T, row.names = T,
        col.names = c("Imputation Method Only", "Additive Model", "Interaction Model"),
        caption = "Logistic fixed-effect regression models for CI coverage rate at the school level") %>%
  kable_classic_2("hover", full_width = F) %>%
  scroll_box(height = "700px")
```

````