---
title: "Source Code for Multiple Imputation Comparisons: Regression Model Vignette"
author: "Allie Cooperman, Adam Van Iwaarden, and Damian Betebenner"
date: "June 16, 2021"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(cache   = FALSE, 
                      eval    = FALSE,
                      echo    = TRUE, 
                      message = FALSE, 
                      warning = FALSE,
                      fig.align = "center") 
```

The code below can be used to recreate the tables and figures in the multiple imputation (MI) regression vignettes. For more information on fitting fixed-effects models with the `fixest` package, see the [`fixest` vignette](https://cran.r-project.org/web/packages/fixest/vignettes/fixest_walkthrough.html).

Note that many of the models are time- and memory-intensive. One may consider setting `cache = TRUE`. Please see Yihui Xie's `knitr` [documentation on caching](https://yihui.org/knitr/options/#cache) for more details. Additionally, it is recommended to routinely remove objects from the R environment (using the `rm()` function) to prevent running out of memory.

The vignettes include a series of regression models that differ by the dependent variable used, unit of analysis (grade/content area or school level), and so forth. For simplicity, we present select example code for a handful of models. This code can be easily modified for additional analyses (e.g., using SGP raw bias rather than scale score raw bias). 

## Set-Up

The code below generates the vignette for the simulated data without a COVID-19 impact. Given that the MI methods differed between the "impact" and "no impact" simulations, make sure to change the data names and imputation method labels accordingly. Additionally, data tables are created across all amputations (`Amp_Level`) and when aggregating across amputed data sets (`Evaluation`). The latter tables, noted by `.Eval`, are used for the mixed-effects models.

````md
```{r setup}`r ''`
# knitr options
knitr::opts_chunk$set(cache   = FALSE, 
                      echo    = FALSE, 
                      fig.align = "center",
                      fig.width = 9,
                      fig.topcaption = TRUE)

# kable options
options(knitr.kable.NA = '')

# Set working directory
setwd("./FilePath")

# Load R libraries
require(pacman)
pacman::p_load(kableExtra, ggplot2, data.table, fixest, lme4)

# Missingness percentages
missperc = c(30, 50, 70)

# Missingness types
misstype = c("MCAR", "STATUS_w_DEMOG", "STATUS_w_GROWTH")

# For-loop to create full data tables
MIsummary.GC = MIsummary.School =  NULL
MIsummary.GC.Eval = MIsummary.School.Eval =  NULL
for(mp in missperc) {
  
  for(mt in misstype) {
    
    # Create file path
    fp = paste0(datadir, "/", mp, " Percent Missing/", mt, "/")
    
    # Load summary data
    load(paste0(fp, "L2PAN_Summaries.rda"))
    load(paste0(fp, "L2PAN_LONG_Summaries.rda"))
    load(paste0(fp, "L2LMER_Summaries.rda"))
    load(paste0(fp, "L2LMER_LONG_Summaries.rda"))
    load(paste0(fp, "PMM_Summaries.rda"))
    load(paste0(fp, "RQ_Summaries.rda"))
    
    # Create "observed" cases
    Observed.GC = copy(PMM_Summaries[["SCHOOL"]][["GRADE_CONTENT"]][["Amp_Level"]])[,IMP_METHOD:="Observed"]
    Observed.GC[, SS_Raw_Bias := SS_Obs_Raw_Bias]
    Observed.GC[, SGP_Raw_Bias := SGP_Obs_Raw_Bias]
    Observed.GC[, SGPB_Raw_Bias := SGPB_Obs_Raw_Bias]
    
    Observed.GC.Eval = copy(PMM_Summaries[["SCHOOL"]][["GRADE_CONTENT"]][["Evaluation"]])[,IMP_METHOD:="Observed"]
    Observed.GC.Eval[, SS_Raw_Bias := SS_Obs_Raw_Bias]
    Observed.GC.Eval[, SGP_Raw_Bias := SGP_Obs_Raw_Bias]
    Observed.GC.Eval[, SGPB_Raw_Bias := SGPB_Obs_Raw_Bias]
    
    Observed.School = copy(PMM_Summaries[["SCHOOL"]][["GLOBAL"]][["Amp_Level"]])[,IMP_METHOD:="Observed"]
    Observed.School[, SS_Raw_Bias := SS_Obs_Raw_Bias]
    Observed.School[, SGP_Raw_Bias := SGP_Obs_Raw_Bias]
    Observed.School[, SGPB_Raw_Bias := SGPB_Obs_Raw_Bias]
    
    Observed.School.Eval = copy(PMM_Summaries[["SCHOOL"]][["GLOBAL"]][["Evaluation"]])[,IMP_METHOD:="Observed"]
    Observed.School.Eval[, SS_Raw_Bias := SS_Obs_Raw_Bias]
    Observed.School.Eval[, SGP_Raw_Bias := SGP_Obs_Raw_Bias]
    Observed.School.Eval[, SGPB_Raw_Bias := SGPB_Obs_Raw_Bias]
    
    # Create long data.table combining imputation methods 
    # By grade/content area
    data.temp.gc = rbindlist(list(
      
      # L2PAN
      data.table(L2PAN_Summaries$SCHOOL$GRADE_CONTENT$Amp_Level, "IMP_METHOD" = "L2PAN"),
      
      # L2PAN LONG
      data.table(L2PAN_LONG_Summaries$SCHOOL$GRADE_CONTENT$Amp_Level, "IMP_METHOD" = "L2PAN_LONG"),
      
       # L2LMER
      data.table(L2LMER_Summaries$SCHOOL$GRADE_CONTENT$Amp_Level, "IMP_METHOD" = "L2LMER"),
      
      # L2LMER LONG
      data.table(L2LMER_LONG_Summaries$SCHOOL$GRADE_CONTENT$Amp_Level, "IMP_METHOD" = "L2LMER_LONG"),
      
      # PMM
      data.table(PMM_Summaries$SCHOOL$GRADE_CONTENT$Amp_Level, "IMP_METHOD" = "PMM"),
      
      # RQ
      data.table(RQ_Summaries$SCHOOL$GRADE_CONTENT$Amp_Level, "IMP_METHOD" = "RQ"),
      
      # Observed
      data.table(Observed.GC))
  
      )
    data.temp.gc.eval = rbindlist(list(
      
      # L2PAN
      data.table(L2PAN_Summaries$SCHOOL$GRADE_CONTENT$Evaluation, "IMP_METHOD" = "L2PAN"),
      
      # L2PAN LONG
      data.table(L2PAN_LONG_Summaries$SCHOOL$GRADE_CONTENT$Evaluation, "IMP_METHOD" = "L2PAN_LONG"),
      
       # L2LMER
      data.table(L2LMER_Summaries$SCHOOL$GRADE_CONTENT$Evaluation, "IMP_METHOD" = "L2LMER"),
      
      # L2LMER LONG
      data.table(L2LMER_LONG_Summaries$SCHOOL$GRADE_CONTENT$Evaluation, "IMP_METHOD" = "L2LMER_LONG"),
      
      # PMM
      data.table(PMM_Summaries$SCHOOL$GRADE_CONTENT$Evaluation, "IMP_METHOD" = "PMM"),
      
      # RQ
      data.table(RQ_Summaries$SCHOOL$GRADE_CONTENT$Evaluation, "IMP_METHOD" = "RQ"),
      
      # Observed
      data.table(Observed.GC.Eval))
  
      )
    
    # Convert imputation method, grade, and content area variables to class "factor"
    data.temp.gc[, IMP_METHOD := factor(IMP_METHOD, 
                   levels = rev(c("Observed", "PMM", "RQ", "L2PAN", 
                                  "L2LMER", "L2PAN_LONG", "L2LMER_LONG")))]
    data.temp.gc[, GRADE := as.factor(GRADE)]
    data.temp.gc[, CONTENT_AREA := as.factor(CONTENT_AREA)]
    data.temp.gc.eval[, IMP_METHOD := factor(IMP_METHOD, 
                        levels = rev(c("Observed", "PMM", "RQ", "L2PAN", 
                                       "L2LMER", "L2PAN_LONG", "L2LMER_LONG")))]
    data.temp.gc.eval[, GRADE := as.factor(GRADE)]
    data.temp.gc.eval[, CONTENT_AREA := as.factor(CONTENT_AREA)]
    
    # Create missingness type and percentage variables
    data.temp.gc[, MISS_TYPE := mt]
    data.temp.gc[, MISS_PERC := mp]
    data.temp.gc.eval[, MISS_TYPE := mt]
    data.temp.gc.eval[, MISS_PERC := mp]
    
    # Combine with previous data
    MIsummary.GC = rbind(MIsummary.GC, data.temp.gc)
    MIsummary.GC.Eval = rbind(MIsummary.GC.Eval, data.temp.gc.eval)
    
    # Create long data.table combining imputation methods 
    # By school
    data.temp.sc = rbindlist(list(
      
      # L2PAN
      data.table(L2PAN_Summaries$SCHOOL$GLOBAL$Amp_Level, "IMP_METHOD" = "L2PAN"),
      
      # L2PAN LONG
      data.table(L2PAN_LONG_Summaries$SCHOOL$GLOBAL$Amp_Level, "IMP_METHOD" = "L2PAN_LONG"),
      
       # L2LMER
      data.table(L2LMER_Summaries$SCHOOL$GLOBAL$Amp_Level, "IMP_METHOD" = "L2LMER"),
      
      # L2LMER LONG
      data.table(L2LMER_LONG_Summaries$SCHOOL$GLOBAL$Amp_Level, "IMP_METHOD" = "L2LMER_LONG"),
      
      # PMM
      data.table(PMM_Summaries$SCHOOL$GLOBAL$Amp_Level, "IMP_METHOD" = "PMM"),
      
      # RQ
      data.table(RQ_Summaries$SCHOOL$GLOBAL$Amp_Level, "IMP_METHOD" = "RQ"),
      
      # Observed
      data.table(Observed.School))
  
      )
    data.temp.sc.eval = rbindlist(list(
      
      # L2PAN
      data.table(L2PAN_Summaries$SCHOOL$GLOBAL$Evaluation, "IMP_METHOD" = "L2PAN"),
      
      # L2PAN LONG
      data.table(L2PAN_LONG_Summaries$SCHOOL$GLOBAL$Evaluation, "IMP_METHOD" = "L2PAN_LONG"),
      
       # L2LMER
      data.table(L2LMER_Summaries$SCHOOL$GLOBAL$Evaluation, "IMP_METHOD" = "L2LMER"),
      
      # L2LMER LONG
      data.table(L2LMER_LONG_Summaries$SCHOOL$GLOBAL$Evaluation, "IMP_METHOD" = "L2LMER_LONG"),
      
      # PMM
      data.table(PMM_Summaries$SCHOOL$GLOBAL$Evaluation, "IMP_METHOD" = "PMM"),
      
      # RQ
      data.table(RQ_Summaries$SCHOOL$GLOBAL$Evaluation, "IMP_METHOD" = "RQ"),
      
      # Observed
      data.table(Observed.School.Eval))
  
      )
    
    # Convert imputation method, grade, and content area variables to class "factor"
    data.temp.sc[, IMP_METHOD := factor(IMP_METHOD, 
                   levels = rev(c("Observed", "PMM", "RQ", "L2PAN", 
                                  "L2LMER", "L2PAN_LONG", "L2LMER_LONG")))]
    data.temp.sc.eval[, IMP_METHOD := factor(IMP_METHOD, 
                        levels = rev(c("Observed", "PMM", "RQ", "L2PAN", 
                                        "L2LMER", "L2PAN_LONG", "L2LMER_LONG")))]
    
    # Create missingness type and percentage variables
    data.temp.sc[, MISS_TYPE := mt]
    data.temp.sc[, MISS_PERC := mp]
    data.temp.sc.eval[, MISS_TYPE := mt]
    data.temp.sc.eval[, MISS_PERC := mp]
    
    # Combine with previous data
    MIsummary.School = rbind(MIsummary.School, data.temp.sc)
    MIsummary.School.Eval = rbind(MIsummary.School.Eval, data.temp.sc.eval)
        
  } # end for mt in misstype
  
} # end for mp in missperc

# Convert missing type and percentage to factor variables
MIsummary.GC[, MISS_TYPE := as.factor(MISS_TYPE)]
MIsummary.GC[, MISS_PERC := as.factor(MISS_PERC)]
MIsummary.GC[, SCHOOL_NUMBER := as.factor(SCHOOL_NUMBER)]
MIsummary.School[, MISS_TYPE := as.factor(MISS_TYPE)]
MIsummary.School[, MISS_PERC := as.factor(MISS_PERC)]
MIsummary.School[, SCHOOL_NUMBER := as.factor(SCHOOL_NUMBER)]
MIsummary.GC.Eval[, MISS_TYPE := as.factor(MISS_TYPE)]
MIsummary.GC.Eval[, MISS_PERC := as.factor(MISS_PERC)]
MIsummary.GC.Eval[, SCHOOL_NUMBER := as.factor(SCHOOL_NUMBER)]
MIsummary.School.Eval[, MISS_TYPE := as.factor(MISS_TYPE)]
MIsummary.School.Eval[, MISS_PERC := as.factor(MISS_PERC)]
MIsummary.School.Eval[, SCHOOL_NUMBER := as.factor(SCHOOL_NUMBER)]

# Create releveled imputation method factor variable
# Setting "Observed" as the reference level for modeling
MIsummary.GC[, IMP_METHOD_REF := relevel(IMP_METHOD, ref = "Observed")]
MIsummary.School[, IMP_METHOD_REF := relevel(IMP_METHOD, ref = "Observed")]
MIsummary.GC.Eval[, IMP_METHOD_REF := relevel(IMP_METHOD, ref = "Observed")]
MIsummary.School.Eval[, IMP_METHOD_REF := relevel(IMP_METHOD, ref = "Observed")]

# Remove observations with N < 10
MIsummary.GC = MIsummary.GC[N >= 10]
MIsummary.School = MIsummary.School[N >= 10]
MIsummary.GC.Eval = MIsummary.GC.Eval[N >= 10]
MIsummary.School.Eval = MIsummary.School.Eval[N >= 10]
setkey(MIsummary.GC, IMP_METHOD); setkey(MIsummary.School, IMP_METHOD)
setkey(MIsummary.GC.Eval, IMP_METHOD); setkey(MIsummary.School.Eval, IMP_METHOD)

# Scale N and percent missing
MIsummary.GC[, Pct_Miss_Raw := Percent_Missing]
MIsummary.GC[, Percent_Missing := scale(Percent_Missing), keyby = c("CONTENT_AREA","GRADE")]
MIsummary.GC[, N_Raw := N]
MIsummary.GC[, N := scale(N), keyby = c("CONTENT_AREA","GRADE")]
MIsummary.GC.Eval[, Pct_Miss_Raw := Percent_Missing]
MIsummary.GC.Eval[, Percent_Missing := scale(Percent_Missing), keyby = c("CONTENT_AREA","GRADE")]
MIsummary.GC.Eval[, N_Raw := N]
MIsummary.GC.Eval[, N := scale(N), keyby = c("CONTENT_AREA","GRADE")]

MIsummary.School[, Pct_Miss_Raw := Percent_Missing]
MIsummary.School[, Percent_Missing := scale(Percent_Missing)]
MIsummary.School[, N_Raw := N]
MIsummary.School[, N := scale(N)]
MIsummary.School.Eval[, Pct_Miss_Raw := Percent_Missing]
MIsummary.School.Eval[, Percent_Missing := scale(Percent_Missing)]
MIsummary.School.Eval[, N_Raw := N]
MIsummary.School.Eval[, N := scale(N)]

# Create percent bias variables
MIsummary.GC[, SS_Pct_Bias := 100*(abs(SS_Raw_Bias/Mean_SS_Complete))]
MIsummary.GC[, SGP_Pct_Bias := 100*(abs(SGP_Raw_Bias/Mean_SGP_Complete))]
MIsummary.GC[, SGPB_Pct_Bias := 100*(abs(SGPB_Raw_Bias/Mean_SGPB_Complete))]
MIsummary.School[, SS_Pct_Bias := 100*(abs(SS_Raw_Bias/Mean_SS_Complete))]
MIsummary.School[, SGP_Pct_Bias := 100*(abs(SGP_Raw_Bias/Mean_SGP_Complete))]
MIsummary.School[, SGPB_Pct_Bias := 100*(abs(SGPB_Raw_Bias/Mean_SGPB_Complete))]
MIsummary.GC.Eval[, SS_Pct_Bias := 100*(abs(SS_Raw_Bias/Mean_SS_Complete))]
MIsummary.GC.Eval[, SGP_Pct_Bias := 100*(abs(SGP_Raw_Bias/Mean_SGP_Complete))]
MIsummary.GC.Eval[, SGPB_Pct_Bias := 100*(abs(SGPB_Raw_Bias/Mean_SGPB_Complete))]
MIsummary.School.Eval[, SS_Pct_Bias := 100*(abs(SS_Raw_Bias/Mean_SS_Complete))]
MIsummary.School.Eval[, SGP_Pct_Bias := 100*(abs(SGP_Raw_Bias/Mean_SGP_Complete))]
MIsummary.School.Eval[, SGPB_Pct_Bias := 100*(abs(SGPB_Raw_Bias/Mean_SGPB_Complete))]

# Set color-blind friendly color palette
# https://stackoverflow.com/questions/65013406/how-to-generate-30-distinct-colors-that-are-color-blind-friendly
colorpal = c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```
````

## Fixed-Effects Models

Below is the code for fitting fixed-effect regression models for scale score raw bias, either at the grade/content area or school level.

````md
```{r}`r ''`
# Fit additive model, grade/content area level
rawbias.ss.allgrades = feols(
  
  # Model formula
  SS_Raw_Bias ~ i(IMP_METHOD_REF) + N + Percent_Missing + MISS_TYPE |
  
  # Fixed effects
  CONTENT_AREA^GRADE + AMP_N,
  
  # Data
  MIsummary.GC,
  
  # Don't combine fixed effects
  combine.quick = FALSE
  
)

# Fit two-way interaction model, grade/content area level
rawbias.ss.interaction.allgrades = feols(
  
  # Model formula
  SS_Raw_Bias ~ i(IMP_METHOD_REF) + (N + Percent_Missing + MISS_TYPE)^2 |
  
  # Fixed effects
  CONTENT_AREA^GRADE + AMP_N,
  
  # Data
  MIsummary.GC,
  
  # Don't combine fixed effects
  combine.quick = FALSE
  
)
```

```{r echo = FALSE}`r ''`
# Print table of models
etable(rawbias.ss.allgrades, rawbias.ss.interaction.allgrades,
       fitstat = c("r2", "war2", "aic", "bic"), subtitles = c("Additive", "Interaction"))[-c(1:2),] %>%
kable(format = "html", booktabs = T, row.names = T,
      col.names = c("Additive Model", "Interaction Model"),
      caption = "Fixed-effect regression models for scale score raw bias at the grade/content area level, all grade levels") %>%
  kable_classic_2("hover", full_width = F) %>%
  scroll_box(height = "500px")
```

```{r echo = FALSE, fig.cap = "Coefficient plot, additive models for scale score raw bias at the grade/content area level"}`r ''`
# Coefficient plots
coefplot(rawbias.ss.allgrades, main = " ", 
         xlab = "Predictor", ylab = "Coefficient Estimate and 95% CI",
         col = colorpal, cex.lab = 0.5)
abline(h = -mean(MIsummary.GC[IMP_METHOD == "Observed", SS_Raw_Bias], na.rm=T), 
       col = "red", lty = "dashed")
```

```{r echo = FALSE, ffig.cap = "Fixed effects estimates, additive model"}`r ''`
# Plot of fixed effects
plot(fixef(rawbias.ss.allgrades))
```

```{r echo = FALSE, fig.cap = "Fixed effects estimates, interaction model"}`r ''`
# Plot of fixed effects
plot(fixef(rawbias.ss.interaction.allgrades))
```

```{r}`r ''`
# Fit additive model, school level
rawbias.ss.school = feols(
  
  # Model formula
  SS_Raw_Bias ~ i(IMP_METHOD_REF) + N + Percent_Missing + MISS_TYPE |
  
  # Fixed effects
  AMP_N,
  
  # Data
  MIsummary.School,
  
  # Don't combine fixed effects
  combine.quick = FALSE
  
)

# Fit two-way interaction model, school level
rawbias.ss.interaction.school = feols(
  
  # Model formula
  SS_Raw_Bias ~ i(IMP_METHOD_REF) + (N + Percent_Missing + MISS_TYPE)^2 |
  
  # Fixed effects
  AMP_N,
  
  # Data
  MIsummary.School,
  
  # Don't combine fixed effects
  combine.quick = FALSE
  
)
```

```{r echo = FALSE}`r ''`
# Print table of models
etable(rawbias.ss.school, rawbias.ss.interaction.school,
       fitstat = c("r2", "war2", "aic", "bic"), subtitles = c("Additive", "Interaction"))[-c(1:2),] %>%
kable(format = "html", booktabs = T, row.names = T,
      col.names = c("Additive Model", "Interaction Model"),
      caption = "Fixed-effect regression models for scale score raw bias at the school level") %>%
  kable_classic_2("hover", full_width = F) %>%
  scroll_box(height = "500px")
```

```{r echo = FALSE, fig.cap = "Coefficient plot, additive models for scale score raw bias at the school level"}`r ''`
# Coefficient plots
coefplot(rawbias.ss.school, main = " ", 
         xlab = "Predictor", ylab = "Coefficient Estimate and 95% CI",
         col = colorpal, cex.lab = 0.5)
abline(h = -mean(MIsummary.School[IMP_METHOD == "Observed", SS_Raw_Bias], na.rm=T), 
       col = "red", lty = "dashed")
```

```{r echo = FALSE, fig.cap = "Fixed effects estimates, additive model"}`r ''`
# Plot of fixed effects
plot(fixef(rawbias.ss.school))
```

```{r echo = FALSE, fig.cap = "Fixed effects estimates, interaction model"}`r ''`
# Plot of fixed effects
plot(fixef(rawbias.ss.interaction.school))
```
````

## Mixed-Effects models

The code below fits an additive mixed-effects model with a random intercept for school. Again, the dependent variable is scale score raw bias, modeling at the grade/content area level.

````md
```{r}`r ''`
# Fit random intercept model
rawbias.ss.lmer = lmer(SS_Raw_Bias ~ IMP_METHOD_REF + N + Percent_Missing + MISS_TYPE + 
                                     GRADE + CONTENT_AREA + (1 | SCHOOL_NUMBER),
                       data = MIsummary.GC.Eval, REML = TRUE)

# Model summary
summary(rawbias.ss.lmer)
```
````